Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-15 main.tex
Multi model extension

@@

@@

@@

The procedure we developed in sections relies on several modelling assumptions which can be quite restrictive, such as the system dynamics \eqref{eq:dynamics} or its linear parametrisation in \autoref{assumpt:linear_param}. But what if they are wrong?

@@

We can test the model adequacy, and eventually reject it.

This suggest using multiple models with different sets of features.

>>>>

\label{sec:estimation}

@@

\label{sec:prediction}

@@

\label{sec:control}

@@

The procedure we developed in sections \ref{sec:estimation}, \ref{sec:prediction} and \ref{sec:control} relies on several modelling assumptions, such as the system dynamics \eqref{eq:dynamics} or \autoref{assumpt:linear_param}. But what if they are wrong?

@@

One of the major benefits of using the family of linear models compared to richer classes is that it enables to measure empirically the adequacy of the modelling assumptions to capture the observed signal,  and thus to raise an alert when the adequacy is too low.

We define the model adequacy for an observation $y$ at point $x$ of the modelling assumptions $(A, \phi)$ trained on history $\cD$.
A value of 1 indicates no mismatch, while a value of 0 indicates a strong mismatch.

This is especially relevant in the context of model selection or aggregation.
This suggest using multiple models with different sets of features.
